Co-evolution of lexical meaning \& pragmatic use

### 2018-01-14 paper/cogsci-submission2.tex
small modifications + new barh plots

\subsection{Example}\label{subsec:example}
Section~\ref{sec:si-case-study} shows how these components and their interaction can shed light on the evolution of scalar implicatures. Before moving on, we will illustrate the model's workings in a constrained type space in order to showcase the effect that pressure for communicative success and learnability have on types. To this end, we focus only on the four types from Section~\ref{sec:languages+use}. These types are made up of a combination of either lexicon $\Llack$ or $\Lbound$ and either literal (level-$0$) or pragmatic (level-$1$) behavior.

@@

\begin{figure}[t]
\centering
\includegraphics[width=\textwidth,height=8cm, keepaspectratio]{./plots/alt-fig1-onlyr}
\caption{Proportion of target types, \hl{pragmatic} competitor types, \hl{pragmatic} $\Lall$, and the population's majority type, in representative populations after $50$ generations under only a
  pressure for communicative success. \hl{Flip plots, change plot generation to show the highest 6 Lbound users and the highest Lall, irrespective of ling. behavior, change text surrounding these things}}
\label{fig:only-R}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\textwidth,height=8cm,keepaspectratio]{./plots/alt-fig2-onlym-pr}
\caption{Proportion of target types, \hl{pragmatic competitor} types, \hl{pragmatic} $\Lall$, and the population's majority type in representative populations after $50$ generations under only a
  pressure for learnability ($\lambda = 20, k = 5$). The learning prior is shown in the
  right-most plot with top-most groupings corresponding to types, literal and pragmatic, with
  lexica of kinds $\Llack$, $\Lbound$, and $\Lall$.}
\label{fig:only-M}
\end{figure}

>>>>

\subsection{Example}\label{subsec:example}
\hl{Mention that x,y independent}
Section~\ref{sec:si-case-study} shows how these components and their interaction can shed light on the evolution of scalar implicatures. Before moving on, we will illustrate the model's workings in a constrained type space in order to showcase the effect that pressure for communicative success and learnability have on types. To this end, we focus only on the four types from Section~\ref{sec:languages+use}. These types are made up of a combination of either lexicon $\Llack$ or $\Lbound$ and either literal (level-$0$) or pragmatic (level-$1$) behavior.

@@

\begin{figure}[t]
\centering
%\includegraphics[width=\textwidth,height=8cm, keepaspectratio]{./plots/alt-fig1-onlyr}
\includegraphics[width=\textwidth,height=8cm, keepaspectratio]{./plots/barh-onlyr}
\caption{Proportion of target types, \hl{pragmatic} competitor types, \hl{pragmatic} $\Lall$, and the population's majority type, in representative populations after $50$ generations under only a
  pressure for communicative success. \hl{Flip plots, change plot generation to show the highest 6 Lbound users and the highest Lall, irrespective of ling. behavior, change text surrounding these things}}
\label{fig:only-R}
\end{figure}

@@

\begin{figure}[t]
\centering
%\includegraphics[width=1\textwidth,height=8cm,keepaspectratio]{./plots/alt-fig2-onlym-pr}
\includegraphics[width=1\textwidth,height=8cm,keepaspectratio]{./plots/barh-onlym}

\caption{Proportion of target types, \hl{pragmatic competitor} types, \hl{pragmatic} $\Lall$, and the population's majority type in representative populations after $50$ generations under only a
  pressure for learnability ($\lambda = 20, k = 5$). The learning prior is shown in the
  right-most plot with top-most groupings corresponding to types, literal and pragmatic, with
  lexica of kinds $\Llack$, $\Lbound$, and $\Lall$.}
\label{fig:only-M}
\end{figure}
